%%%%%%
%%
%%  Don't reorder the reviewer points; that'll mess up the automatic referencing!
%%
%%%%%

\begin{minipage}[b]{2.5in}
  Resubmission Cover Letter \\
  {\it Theoretical Population Biology}
\end{minipage}
\hfill
\begin{minipage}[b]{2.5in}
    Peter Ralph \\
  \today
\end{minipage}
 
\vskip 2em
 
\noindent
{\bf To the Editor(s) -- }
 
\vskip 1em

We are writing to submit a revised version of our manuscript,
``Looking forwards and backwards: dynamics and
genealogies of locally regulated populations''.
Thanks to the reviewer's comments
(as well as separate comments from Mattias Birkner),
we think the manuscript has been improved and clarified in a number of places,
a few (happily, relatively minor) errors and omissions
have been fixed,
and the manuscript is generally improved.
We hope you agree.

We have submitted a clean version of the revised paper and
the response to the reviewer as separate PDFs;
line numbers in this response refer to the ``clean'' version.
Also, we have submitted a single PDF
with changes to the previous version shown (with latexdiff)
and a version of the response to reviewer at the end of the document.
In this combined ``diff''document, line numbers (and hyperlinks)
in the reviewer responses are consistent within the document.

\vskip 2em

\noindent \hspace{4em}
\begin{minipage}{3in}
\noindent
{\bf Sincerely,}

\vskip 2em

{\bf 
Peter Ralph
}\\
on behalf of \\
{\bf 
Alison Etheridge,
Tom Kurtz,
Ian Letter,
and Terence Tsui Ho Lung.
}\\
\end{minipage}

\vskip 4em

\pagebreak

%%%%%%%%%%%%%%
\section*{AE comments:}


%%%%%%%%%%%%%%
\reviewersection{1}

\begin{quote}
The authors introduced a class of spatial population models in which individuals have locations
in the continuum space $\IR^d$. The population dynamics is controlled by three quantities: birth,
establishment and death, each of which can depend on the spatial location and local population
density. For a fixed time $t$, the population can be represented by a point measure $\eta_t^N$ in which
each individual is assigned a mass $1/N$, where $N$ is a parameter such that initially there are $O(N)$
individuals per unit volume in $\IR^d$. The population dynamics is represented by a continuous-time
Markov process $(\eta_t^N)_{t\ge0}$. The key feature of this model is that it distinguishes between juveniles
and adults. The authors obtained three different scaling limits for the model $(\eta_t^N)_{t\ge0}$ as $N \to \infty$,
which are super-processes, non-local differential equation and reaction-diffusion type PDE. The
author also obtained a description of the dynamics of a single lineage as $N \to \infty$, when the
limiting population dynamics is deterministic.

A main contribution of this paper is the rigorous derivation of lineage dynamics through the
lookdown construction. The convergence of the population dynamics to super-processes, non-
local PDE and PDE are also significant, as they inform us of not only the limiting object that are
expected to be robust against model perturbation, but also of the corresponding scaling regimes
and parameter combinations for model reduction. The one-step convergence presents a usual technical
challenge about identifying the limit. The authors overcame the challenge masterfully by
establishing continuity estimates that guarantee good agreement for the nonlinear terms between
the limiting PDE and the stochastic model, under high mixing rate and a high density assumption.
Overall, this is a very high quality paper that contains many interesting and novel results to merit
publication in EJP, after minor revision.
\end{quote}

Thanks for the many kind words.
We're glad you enjoyed it.

\subsection*{Major comments}

\begin{point}{\revref}
The first paragraph seems sloppy. For example, this expression [for $\mu_\theta(x)$] is non-negative for
what range of values for $(x, \eta)$? Why ``anyway true for sufficiently large $\theta$''? Perhaps this
assumption should be labeled and called upon whenever is it being referred to.
\end{point}

\reply{
    We've revised this to remove the $\max$ in Equation~\eqref{eqn:mu_defn},
    and make the assumption that this is nonnegative more consistently:
    see \revref{} and the new paragraph following Assumptions~\ref{def:model_setup}.
}

\begin{point}{}
    Definition \ref{def:lineage_generator}, Proposition \ref{thm:lineages}:
    I think these may need to be rewritten/rephrased. Up
to Proposition \ref{thm:lineages}, it is not clear what ``that individual'' is in the limiting model. Therefore,
it is not clear what $L_s$ is. While the definition of the process $L^N$ maybe clear, what is the
precise definition of $L_s$ ? I think these need to be defined through the finite-$N$ models. It may
be good to explain why the process $L$ is Markovian, or at least point out that it is Markovian,
before talking about semigroup. Probably Section \ref{sec:lineage_motion} will need to be modified accordingly.
\end{point}

\reply{
    This is a bit tricky, because really to justify this being a sensible notion
    we'd like to refer to the lookdown, which has not yet been introduced.
    To make things more clear we've added a bit to the earlier introductory paragraph
    \llname{whatis_lineage},
    reworded Definition~\ref{def:lineage_generator} somewhat,
    and added some more explanation after the Definition and before the Proposition,
    which also points out that it is Markovian \revref.
}

\begin{point}{\revref}
The two conditions in equation \eqref{conditions for one step} are crucial for the one-step convergence.
It would be great to mention exactly where each of them are used in Section \ref{subsec:one step convergence proof}.
A brief explanation about these conditions would also be nice. For example, it seems the first (high
migration/mixing rate) condition in \eqref{conditions for one step},
but not the second (high density) condition, is used
to guarantees that $\psi_t^{\epsilon,x}$ is close to a heat kernel?
\end{point}

\reply{
    We've added a bit more here \revref,
    and also referred the reader back to the (at this point long-ago)
    discussion earlier \llname{one_step_heuristics}.
}

\subsection*{Minor comments}

\begin{point}{\revref}
\eqref{eqn:mu_defn}: The authors mentioned ``define the death rate'' and ``where this equation defines F'',
which is confusing. What is being defined here? Please clarify. It seems to me that one has
to first choose $F$, then define $\mu_\theta(x)$ as in \eqref{eqn:mu_defn}.
\end{point}

\reply{
    That's right; we've rearranged this so it's hopefully more clear \revref.
}

\begin{point}{\revref}
% P7, paragraph after Remark 2.3:
``and once there establishes...'' It maybe better to split this
long sentence into two complete sentences.
\end{point}

\reply{
    We've rearranged this to be shorter  \revref.
}

\begin{point}{\revref}
% P7, paragraph after Remark 2.3:
$\meanq(x)$ and $\covq(x)$ did not appear before. Perhaps mention they
are given/chosen, or simply delete them here, and mention them in Definition \ref{def:dispersal_generator}.
\end{point}

\reply{
    That's right, this bit was supposed to introduce those functions
    (and we want to keep them here to emphasize the scaling with $1/\theta$).
    We've rewritten this to make this more clear \revref.
}

\begin{point}{\revref}
Remark \ref{ancestral lineages: first guess}
Why use $m$ in the superscript of $q_\theta^m(x, \eta, dy)$?
\end{point}

\reply{
    We've added a clarifying point \revref.
}

\begin{point}{}
Assumptions \ref{def:model_setup}: Should it be ``Assumption 2.8'' instead? Also, $\alpha$ in condition 1 was
used in $\alpha = lim_{N \to \infty} \theta(N)/N$ on Page 8, Figure 1, etc.
\end{point}

\reply{
    Good question -- it could go either way,
    but since there's more than one assumption, we'd like to keep it plural?
    And, good point about re-use of $\alpha$; we've changed it to 
    ``$\beta$-H\"older continuous for some $\beta \in (0, 1]$''.
}

\begin{point}{\revref}
% P9 last line:
    Should the ``$C$'' on the right hand side of the equal sign [in the equation for $C_f$] be deleted ?
\end{point}

\reply{
    The notation there was supposed to convey what exactly about $f$ the constant $C_f$
    depends on, i.e., it could be defined via a function $C : \IR_{\ge 0} \to \IR_{\ge 0}$
    whose argument is the stuff in the parentheses.
    We could write this out explicitly, but think it's fairly standard to write things this way
    -- if on re-reading it is still confusing, we're happy to change it, though?
}

\begin{point}{\revref}
% P10 paragraph below Lemma 2.9:
    Why ``no longer suffices'', and why this is true? . Please
explain. I don’t seem to find this explained in any remark before this.
\end{point}

\reply{
    We intended the \emph{next} sentence to explain why this is true;
    to make this more clear
    we changed that sentence from
    \emph{``Perhaps the simplest example in which we can see this is the case''}
    to
    \emph{``Perhaps the simplest example in which we can see
    that non-local reproduction can lead to rapid growth even when $r\gamma=\mu$''}
    \revref.
}

\begin{point}{}
    Figure \ref{fig:super_vs_det_2d}: What is $N$, the time and other parameters (e.g. $\rho_r$ , $\rho_\gamma$) in the simulations? Same
for other figures. Please at least specify the range of values.
\end{point}

\reply{
    We've added some more detail to the caption.
}

\begin{point}{\revref}
% P12 paragraph after Corollary 2.11:
A more precise reference, or explanation for why
uniqueness holds for this special case would be helpful, as the references you ave are all
quite extensive.
\end{point}

\reply{
    Good suggestion -- this was rather cryptic.
    We've expanded on what we meant here \revref.
}

\begin{point}{}
Proposition \ref{nonlocalPME to PME}:
    It seems the constant $C$ is not needed. Perhaps just say the supremum
of the first displayed expression over $\epsilon$ finite?
\end{point}

\reply{
    Good point! Done.
}

\begin{point}{}
Remark \ref{remark_on_nonlocal_to_local}: Can you explain a bit more why it will be necessary to retain averaging of r?
\end{point}

\reply{
    Good idea; done \revref.
}

\begin{point}{}
% P16: Second paragraph:
The notation $L_t$ seems to first appear here and was not yet defined.
\end{point}

\reply{
    Ah, true - now we introduce it (albeit still informally) earlier \llname{Linf_mention}.
}

\begin{point}{}
% P19-20:
    The equations for the lineage dynamics for the three examples [i.e., Fisher-KPP, Allen-Cahn, and Porous Medium] are interesting.
Which is/are new in this paper, and which was/were known before (and related references)?
\end{point}

\reply{
    As far as we know, the PME case is new,
    but there's been a fair amount of work on FKPP-like
    cases covering the other two cases.
    We've put a note about this, 
    and some pointers to this literature \revref.
}

\begin{point}{}
This maybe out of the scope of this paper, but it is related. As the authors pointed out, two
lineages probably will not coalesce in the limiting model. However, they will coalesce in
the finite-$N$ model, though it may take a very long time. I wonder if the authors have a
feeling about whether the description of the lineage dynamics in the limit still be a good
approximation for that of the finite model for such a long time.
\end{point}

\reply{
    Good question -- we've added a note about this question \revref.
}

\begin{point}{}
The subtitle of section \ref{sec:nonunique_lineage} does not match the actual content in that section. Please
update the subtitle. Also, can you give a reference for the claim in the last sentence in this
section \revref?
\end{point}

\reply{
    We've retitled this section, and added a citation \revref.
}

\begin{point}{\revref}
specify ``this process'' in the line below the first displayed equation in
Section 5.1.
\end{point}

\reply{
    Done \revref.
}

\begin{point}{\revref}
Paragraph starting with ``Levels never cross below 0'': Should it be instead ``Levels never
go above $N$''? If so, what particles are regarded as dead? Perhaps those exit the interval
$[0, N]$? Note that equation \eqref{eqn:dot_u} suggests that levels can now go above $N$.
\end{point}

\reply{
    This was correct as written;
    we've rephrased it to be more clear \revref.
}

\begin{point}{\revref}
``Recall from equation~\eqref{eqn:mu_defn}''
does not seem correct, as there is a max in \eqref{eqn:mu_defn}. Please
correct this.
\end{point}

\reply{
    We've removed the $\max$ in \eqref{eqn:mu_defn}.
}

\begin{point}{\revref}
Please give a precise reference/explanation to why uniqueness holds for the martingale problem for finite $N$.
\end{point}

\reply{
    Done \revref.
}

\begin{point}{\revref}
% P32 third line in Section 5.3:
    Pointwise in time?
\end{point}

\reply{
    We mean for each $\omega$; now clarified \revref.
}

\begin{point}{\revref}
Proposition \ref{prop:limiting_construction}: In ``For any solution to the equation above'', what is a ``solution''? Is it
a solution for all time? Also, be specific to ``the equations above'' by labeling and referring
to the precise equations including the unlabeled displayed equation below \eqref{eqn:limiting_construction}.
\end{point}

\reply{
    Good suggestion; we've clarified, see \revref{} and \llname{XU_clarification}.
}

\begin{point}{}
The word ``Proof'' is missing in ``Proof of Proposition 5.6''. This word is also
missing in other places in Sections 6-8.
\end{point}

\reply{
    Whoops! That was due to a \LaTeX{} format change; now fixed.
}

\begin{point}{}
``Proof of Proposition \ref{prop:limiting_construction}'': Do you also need the unlabeled displayed equation below
\eqref{eqn:limiting_construction}? The solution is for all time.
\end{point}

\reply{
    We think this point was an unedited duplicate of point 1.24 above? (If not, we're not sure what else it's saying?)
}

\begin{point}{\revref}
Be specific about ``these results'' in ``Proof of the remainder of these results...'' Also, at the
very beginning of Remark \ref{remark_on_branching}, Be specific about what ``The process'' is.
\end{point}

\reply{
    Happily, there were no remaining results that we hadn't already said where the proofs were,
    so this line is deleted. We also said that ``the process'' is $\lp$ \revref.
}

\begin{point}{\revref}
``Condition 1'' here is that for Lemma 2.9, not that for Assumptions 2.8. Please specify.
\end{point}

\reply{
    Good point - these were not called ``conditions'' in Lemma~\ref{lem:conditions on r},
    so we now refer to them as ``assumptions'' \revref.
}

\begin{point}{\revref}
Perhaps give a reference to the ``familiar pattern''.
\end{point}

\reply{
    Done \revref.
}

\begin{point}{\revref}
% P40 first displayed equation:
Mention $M_t$ is a martingale for all such test functions.
\end{point}

\reply{
    Done \revref.
}

\begin{point}{\revref}
%    P48:
    The notation $\mathcal{O}(\epsilon)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
    We've made the bounds here (and below) more explicit.
    \revref
}

\begin{point}{\revref}
% P54: near the bottom:
    Can you be more specific what in paper \citet{barlow/jacka/yor:1986} is being used here?
\end{point}

\reply{
    It was Item (4.b'), Table 4.1, p. 162, again --
    we've modified this to hopefully 
    more clearly refer to the previous place we used the same argument
    \revref.
}

\begin{point}{\revref}
% P60:
The notation $\mathcal{O}(\delta)$ seems to first appear here. Please explain its meaning. Do they
depend on $x$?
\end{point}

\reply{
    We've clarified this (but also note that the expression does not depend on $x$) \revref.
}

\begin{point}{\revref}
% P65: Remark 8.1:
measure-values processes $\to$ measure-valued processes
\end{point}

\reply{
    Done. \revref
}

\begin{point}{}
Section \ref{sec:lineages_proof} may need to be modified also based on the second point in ``Major
comments'' above.
\end{point}

\reply{
    Thanks! We didn't think that any modifications were necessary, though.
}

